PAMELA: an annotation-based Java Modeling Framework

### 2021-02-09 architecture.tex
integration of Antoine's changes (blue stuff now black)

\ab{Programmers may already reuse} a number of advanced programming features
(some already mentioned) such as: multiple inheritance and traits, containment
management, cloning, fine-grained notifications management, object graph
comparison and diff/merge, visiting patterns, clipboard management, validation,
support for \emph{design by contract} by integrating assertions from Java
Modeling Language (JML), Metaprogramming, Aspect Oriented Programming. Each of
those features is described on a dedicated page that is reachable from the
official web site\footnote{\url{https://pamela.openflexo.org/SNAPSHOT/}}.
\ab{Experimented programmers may extend PAMELA defining new annotations.}

>>>>

Programmers may already reuse a number of advanced programming features
(some already mentioned) such as: multiple inheritance and traits, containment
management, cloning, fine-grained notifications management, object graph
comparison and diff/merge, visiting patterns, clipboard management, validation,
support for \emph{design by contract} by integrating assertions from Java
Modeling Language (JML), Metaprogramming, Aspect Oriented Programming. Each of
those features is described on a dedicated page that is reachable from the
official web site\footnote{\url{https://pamela.openflexo.org/SNAPSHOT/}}.
Experimented programmers may extend PAMELA defining new annotations.

### 2021-02-09 pamelaProcess.tex
integration of Antoine's changes (blue stuff now black)

\ab{In this presentation, we focus on the programming use of PAMELA, when programmers reuse existing annotations. The full power of PAMELA arises when programmers become modelers defining their own abstractions/annotations.}

>>>>

In this presentation, we focus on the programming use of PAMELA, when programmers reuse existing annotations. The full power of PAMELA arises when programmers become modelers defining their own abstractions/annotations.
